Age-related changes in plant growth and traits

### 2016-11-24 scripts/nutrient.Rmd
starting to think about nutrient concentrations in stems

>>>>

#looking at sequential discs from stems
```{r}
wood_discs_base <- nutrient %>%
    subset(tissue_complete %in% c("wood_from_base"))%>%
    select(individual_rep1,species,P) 
names(wood_discs_base) <- c("individual","species","P_base")

wood_discs_middle <- nutrient %>%
    subset(tissue_complete %in% c("wood_from_middle"))%>%
    select(individual_rep1,P) 
names(wood_discs_middle) <- c("individual","P_mid")

wood_discs_tip <- nutrient %>%
    subset(tissue_complete %in% c("wood_from_tip"))%>%
    select(individual_rep1,P) 
names(wood_discs_tip) <- c("individual","P_tip")

wood_discs <- merge(wood_discs_base, wood_discs_middle, by="individual")
wood_discs <- merge(wood_discs, wood_discs_tip, by="individual")

```
unique(nutrient$tissue_complete)
